\begin{lemma}\label[lemma]{1e4}
Let $\Ip\subset R$ be an prime ideal.
The closed set $V_X(\Ip)$ is irreducible.
This implies that $\counit_X$ is injective.
\end{lemma}
\begin{proof}
Let $\counit_X(z)=\Ip$ for some $z\in X$. By lemma .. this is possible.
So $\ker{z} = \Ip$.
Let $y\in V_X(\Ip)$. Then $\ker(z)\subset \ker(y)$, hence if $y\in D_X(a)$ then $z\in D_X(a)$.
Therefore $z$ is contained in any open subset of $V_X(\Ip)$, hence it is irreducible.
Any element that is send to $\Ip$ will be the generic point of $V_X(\Ip)$.
Uniqueness of generic points implies injectivity of $F$.

\begin{comment}
Let $U \cup V = V_X(\Ip)$ with $U,V$ closed. 
The inclusions $u,v$ of closed sets $U,V$ is a quasi-compact map, because a closed set of a quasi-compact is quasi-compact. 
Therefore $u_*,v_*$ sends quasi-coherent modules to quasi-coherent modules [Reference].

Let $\sheaf{I},\sheaf{J}$ be the ideal sheaves corresponding to the reduced induced subscheme structure $(U,\sheaf{O}_U),(V,\sheaf{O}_V)$
on the closed sets $U$ and $V$. Hence the sequences
\[\sheaf{I}\rightarrow \sheaf{O}_X \rightarrow u_*(\sheaf{O}_U)\rightarrow 0,\]
\[\sheaf{J}\rightarrow \sheaf{O}_X \rightarrow v_*(\sheaf{O}_V)\rightarrow 0\]
are exact and so $\sheaf{I},\sheaf{J}$ are quasi-coherent.
Let $I,J$ be the global sections of $\sheaf{I}$ and $\sheaf{J}$.
Because of our adjoint equivalence $\Lambda_X(I)=\sheaf{I}$ and $\Lambda_X(J)=\sheaf{J}$, hence also $U=V_X(I)$ and $V=V_X(J)$.
We now have $V_X(IJ)=V_X(\Ip)$.
Moreover $\Lambda_X(\frac{\sheaf{O}(X)}{I}) \iso \frac{\sheaf{O}}{\sheaf{I}} \iso u_*(\sheaf{O}_U)$ and similar for $J,v,V$.
Since $\sheaf{O}_U$ is a reduced sheaf, $\sheaf{I}(W)$ is radical for every open $W \subset X$.

Now invoke the previous lemma for both inclusions wrt $IJ$ and $\Ip$. 
This yields $I\cap J = \Ip$, hence $I=\Ip$ or $J=\Ip$.
Now one of the closed sets $U,V$ is the whole of $V_X(\Ip)$.
\end{comment}
\end{proof}