\begin{lemma}
Sheafifying and restricting commute.
In formula form
\[\sheafify_b \circ \restrictOpt{b} \iso \restrictOpt{b} \circ \sheafify_a.\]
\end{lemma}

\begin{proof}
I will prove that we have a natural isomorphism 
\[s : \sheafify_b \circ \restrictOpt{b} \rightarrow \restrictOpt{b} \circ \sheafify_a.\]

Let $\presheaf{F}$ be a presheaf on $\overcat{Y}{a}$.
Let $\sheaf{H} = \sheafify{\restrictOpt{b}{F}}$
and $\sheaf{K} = \restrictOpt{b}{\sheafify{F}}$.
Let $T$ be a covering sieve on $g$ in $\overcat{Y}{b}$
and $j\in T$.
Let $S_j$ be a covering sieve on $\dom{j}$ in $\overcat{Y}{b}$
and $i\in S_j$.

Let $x = (x_{i,j}) \in \sheafify{\restrictOpt{b}{F}}$ 
be indexed by $S_j$ and $T$.
We have $x_{i,j} \in \sections{\dom{i}}{F}$.
Define $s_g(x) = (x_{u(i),u(j)})$ with indexing covering sieves $u(S_j), u(T)$.

\textit{well-definedness}
Let $x \sim y$.
Let $R$ be the covering sieve on which they are the same.
Then $s_g(x) \sim s_g(y)$ because they are the same on $u(R)$.
Hence this map is well-defined.

\textit{injectivity}
Let $s_g(x) = s_g(y)$. Then there is some covering sieve $R$ on $fg$ on which they agree.
Consider $\inverse{u}(R)$ as a covering sieve on $g$ and its is clear that $x$ and $y$ must agree on it,
hence the map is injective.

\textit{surjectivity}
Let $y=(y_{k,l})$ be an element of $\sections{c}{K}$ which is indexed by $V,W$.
Then $s_g(y') = y$ where $y'$ has the same elements as $y$ but is indexed by $u(V), u(W)$,
so $y' \in \sections{c}{H}$. Hence $s_g$ is surjective.

\textit{Naturality}
Let $h: c' \rightarrow b$ and $p: c' \rightarrow c$, such that $gp = h$.
We will show that $s_h\sheaf{H}(t) = \sheaf{K}(t)s_g$. See below diagram.
Let $x = (x_{i,j}) \in \sections{c}{H}$ with indexing covering sieves $S_j$ and $T$.
Then $\sheaf{K}(t)(s_g(x)) = (x_{k,l})$ with indexing covering sieves $t^*S_l$ and $t^*T$.
The other one becomes $s_h(\sheaf{H}(t)(x)) = (x_{k,l})$ with indexing covering sieves $t^*S_l$ and $t^*T$.
Hence $s$ is natural.

%Diagram
\begin{center}
	\begin{tikzcd}[row sep = large, column sep = large]
		\sections{h}{H} \arrow{r}{s_h} 
		& \sections{h}{K}\\
		\sections{g}{H} \arrow{r}{s_g} \arrow{u}{\sheaf{H}(t)}
		& \sections{g}{K} \arrow{u}{\sheaf{K}(t)}
	\end{tikzcd}
\end{center}
\end{proof}