\begin{definition}[Restrictive functor]
A functor  $f:\rsite{C}{T}{O} \rightarrow \rsite{D}{S}{U}$ between ringed sites is called restrictive if for every quasi-coherent module $\module{G}$ the co-unit induces an isomorphism 
\[\module{G} \rightarrow \direct{f}\inverse{f}\module{G},\]
\[\sections{\terminal}{G} \rightarrow \sections{\terminal}{\direct{f}\inverse{f}G} \iso \sections{\terminal}{\inverse{f}G}\]
\[\sections{\terminal}{G}\tensor_{\sections{\terminal}{O}} \sections{\terminal}{U} \rightarrow \direct{f}\inverse{f}\module{G}.\]

Note that 
\end{definition}

\begin{definition}[Restrictive morphism]
A morphism $f:X\rightarrow Y\in \cat{C}$ is called restrictive if the induced functor
\[\overcat{C}{X}\rightarrow \overcat{C}{Y}\] is restrictive.
\end{definition}

\begin{example}
In $\schemes$, the morphism $\Spec{A_f} \rightarrow \Spec{A}$ is restrictive.
%TODO: functor that is restrictive. Yoneda embedding? AffSch in Sch?
\end{example}

\begin{nonexample}
The open immersion $\Spec{R^2}\setminus 0 \rightarrow \Spec{R^2}$ is not restrictive.
The quasi-coherent sheaf $\Lambda(\frac{R[x,y]}{xy})$  fails to satisfy the condition from the definition.
% TODO: right it out completely
\end{nonexample}

\begin{lemma}[Restrictive to affines]
If $f:X\rightarrow \Spec{R}$ is a restrictive open immersion. 
then $X$ is affine.
%TODO: What is an open immersion categorically?
\end{lemma}
\begin{proof}
%TODO
\end{proof}

% Q: Let $X$ be covered by $\Spec{R_{f_i}}$. Let $S$ be the set of these $f_i$ and then multiplicatively closed.
% Make $S$ into a category as in http://math.stackexchange.com/questions/664471/represent-localization-as-a-direct-limit
% Is $X$ the limit over this category?

\begin{nonexample}[Affine non-restrictive map]
Both canonical inclusions $\affspace{i} \rightarrow \projspace{i}$ are not restrictive.
Look at the quasi-coherent module $\sheaf{O}(-1)$. There are no global sections but on every affine chart this invertible sheaf is trivial.
\end{nonexample}

%Q: Is restrictiveness preserved under pullback? 

\begin{nonexample}
Any inclusion $\Spec{\kappa(\Ip)} \rightarrow \projspace{1}$ is not restrictive. Look at $\sheaf{O}(-1)$.
\end{nonexample}

\begin{lemma}
The composition of two restrictive functors is restrictive. If the composition $gf$ is restrictive, then $g$ is restrictive
\end{lemma}
\begin{proof}
%TODO
\end{proof}